Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2022-12-21 Manuscript_rev2-LL.tex
cleaning up figure captions

We consider our dimer from Section~\ref{sec:brownian} in an optical trap; at any point in time we can draw a unit vector $\hat{s}$ that points from the centre of larger sphere, to the centre of the smaller sphere. A plane wave 'probe' laser, directly perpendicular to the trapping laser, is incident on the dimer generating a scattering pattern that is dependent upon the dimer's orientation $I(\hat{\bf s}, \theta)$, computed using MSTM. To represent the experimental set up, four angles  ($\theta_1, \ \theta_2, \ \theta_3, \ \theta_4$) were chosen and the calculated intensity at each angle $\theta_k$ was recorded as $I(\hat{s}, \theta_k)$.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{./Images/fig3.png}
	\caption{Model's estimation of dimer orientation while assuming $p(\hat{\bf n}_\alpha)$ to be uniform. Blue line denotes the best result we can achieve, orange line denotes the result provided by eq~\ref{eq:bayes}. Dotted line denotes maximum spacing between two neighbouring $\hat{\bf n}_\alpha$, see Sec~\ref{sec:Bayes}.}
	\label{fig:uniform}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{./Images/fig4.png}
	\caption{Model's estimation of dimer orientation with $p(\hat{\bf n}_\alpha)$ being defined by Eq~\eqref{eq:boltz}. Blue line denotes the best result we can achieve, orange line denotes the result provided by eq~\ref{eq:bayes}. Dotted line denotes maximum spacing between two neighbouring $\hat{\bf n}_\alpha$, see Sec~\ref{sec:Bayes}.}
	\label{fig:biased}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{./Images/fig5a.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig5b.png}
	\end{subfigure}
	\caption{Simulation results of: (a) the dimers orientation vector with time, (b) the dimer's [x,y,z] position with time.}
	\label{fig:motion}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig6a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig6b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig6c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of (a) $1\%$ ~  $[F(K_l)=1.174]$, (b) $15\%$ ~ [$[F(K_l)=0.606]$, and (c) $25\%$ ~  $[F(K_l)=0.457]$.}
	\label{fig:epsilon}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig7a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig7b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig7c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of $1\%$, $15\%$, and $25\%$ with (a) $\beta=4$ ~ $[F(K_l)=1.914]$, (b) $\beta=15$ ~  $[F(K_l)=0.734]$, and (c) $\beta=22$ ~ $[F(K_l)=0.621]$.} 
	\label{fig:beta}
\end{figure}

>>>>

We consider our dimer from Section~\ref{sec:brownian} in an optical
trap; at any point in time we can draw a unit vector $\hat{\bf s}$
that points from the centre of larger sphere, to the centre of the
smaller sphere.  A plane wave 'probe' laser, directly perpendicular to
the trapping laser, is incident on the dimer generating a scattering
pattern that is dependent upon the dimer's orientation
$I(\hat{\bf s}, \theta)$, computed using MSTM. To represent the
experimental set up, four angles
$(\theta_1, \theta_2, \theta_3, \theta_4)$ were chosen and the
calculated intensity at each angle $\theta_k$ was recorded as
$I(\hat{s}, \theta_k)$.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{./Images/fig3.png}
\caption{\label{fig:uniform}
%
Estimation of the dimer orientation, assuming $p(\hat{\bf n}_\alpha)$
to be uniform. Blue line denotes the best result we can achieve,
orange line denotes the result provided by eq~\ref{eq:bayes}. Dotted
line denotes spacing between two neighbouring
reference orientations $\hat{\bf n}_\alpha$ (see Section~\ref{sec:Bayes}).
%
}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{./Images/fig4.png}
\caption{\label{fig:biased}
%
Estimation of dimer orientation with $p(\hat{\bf n}_\alpha)$ defined
by Eq~\eqref{eq:boltz}.  Blue line denotes the best result we can
achieve, orange line denotes the result provided by eq~\ref{eq:bayes}.
Dotted line denotes spacing between two neighbouring reference
orientations $\hat{\bf n}_\alpha$ (see Section~\ref{sec:Bayes}).
  %
}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{subfigure}{0.45\textwidth}
	\subcaption{}
	\includegraphics[width =\textwidth]{./Images/fig5a.png}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth]{./Images/fig5b.png}
\end{subfigure}
\caption{\label{fig:motion}
%
Simulation results of: (a) the dimers orientation vector with time,
(b) the dimer's [x,y,z] position with time.
%
}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{subfigure}{0.32\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth]{./Images/fig6a.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth]{./Images/fig6b.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth]{./Images/fig6c.png}
\end{subfigure}
\caption{\label{fig:epsilon}
%
Model prediction for signal error of (a) $1\%$ ~ $[F(K_l)=1.174]$, (b)
$15\%$ ~ [$[F(K_l)=0.606]$, and (c) $25\%$ ~ $[F(K_l)=0.457]$.
%
}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{subfigure}{0.32\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth]{./Images/fig7a.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth]{./Images/fig7b.png}
\end{subfigure}
\begin{subfigure}{0.32\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth]{./Images/fig7c.png}
\end{subfigure}
\caption{\label{fig:beta}
%
  Model prediction for signal error of $1\%$, $15\%$, and $25\%$ with (a) $\beta=4$ ~ $[F(K_l)=1.914]$, (b) $\beta=15$ ~  $[F(K_l)=0.734]$, and (c) $\beta=22$ ~ $[F(K_l)=0.621]$.
%
} 
\end{figure}
